---
title: "SC Model Results Summary"
output: 
  html_document:
params:
  model.results: "C:/Hatfield/scripts/R/Projects/Meso/occupancy/OccEstimatesbyYear/data/out/SC_results_files_2017/SC_fm_results_2017_AmericanBadger_20200410.Rdata"
  model.year: "2017"
  model.species: "AmericanBadger"
  model.meta: "C:/Hatfield/scripts/R/Projects/Meso/occupancy/OccEstimatesbyYear/data/out/SC_results_files_2017/metadata/SC_model_meta_2017.Rdata"
---

```{r, include=F}
## will probably have to do one file per study season, tricky to generalize across years..
## 

  # html_document:
  #   keep_md: TRUE

library('mcmcplots')
library('coda')
library('ggmcmc')
library('tidyverse')
library(bayestestR)
library(knitr)
library(kableExtra)
library(gridExtra)
library(logspline)
#library(nimble)

catch.p_map<-function(x){
  tryCatch({
   round(p_map(x),5)
}, warning = function(w) {
    ""
}, error = function(e) {
    "err"
})
}

catch.map_estimate<-function(x){
  tryCatch({
   round(map_estimate(x),3)
}, warning = function(w) {
    ""
}, error = function(e) {
    "err"
})
}
# Mode <- function(x) {
#   ux <- unique(x)
#   ux[which.max(tabulate(match(x, ux)))]
# }
# 
# 
# Modes <- function(x) {
#     ux <- unique(x)
#     tab <- tabulate(match(x, ux))
#     ux[tab == max(tab)]
# }

model.results<-readRDS(params$model.results)
 #model.results <- params$model.results

#model.dat<-params$model.results
# getwd()
meta<- readRDS(params$model.meta)
#meta<-readRDS("../../data/out/SC_model_meta_2017.Rdata")
# names(meta)

models <- c(unlist(meta$inputModels))
descriptions<- c(unlist(meta$models))
n<-sum(c(unlist(meta$all.y.long[names(meta$all.y.long) %in% params$model.species])))
M <- meta$M
n.iter<-meta$n.iter
n.burn<-meta$n.burn
state.buffer<-meta$buffer
nSites<-meta$nSites
meta$mean.sd
names(model.results)<-models

meta.summary<-tibble(n_sites = nSites, N_detections = n, rep_period = '7 days', model_agg_M = M, iterations = n.iter, burnin = n.burn, state_buffer = state.buffer)


if(params$model.year == '2016'){
  model.site <- 'SN east side cells'
}else if(params$model.year == '2017'){
  model.site <- 'Humphreys Basin'
}else if(params$model.year == '2018'){
   model.site <- 'Mono creek'
}else if(params$model.year == '2019'){
  model.site <- 'Ritter Range'
}else{
  model.site <- '*****'
}

```
<br><br><br><br/>

#### Year: &nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; `r params$model.year`
#### Species:  &nbsp;&nbsp;&nbsp;&nbsp;  `r params$model.species`
#### Study Site:  &nbsp;&nbsp;  `r model.site`




<br><br/>

#### Metadata Summary:
```{r, echo = F}
## look at the metadata
kable(meta.summary,align = 'c') %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")



```

<br><br/>

#### WAIC
Models by WAIC:
```{r, echo = F}
### first look at the models by waic:

models.waic<-c(unlist(lapply(model.results, function(x) x$WAIC)))
waic.table<-tibble(model = models, description = descriptions, WAIC = models.waic) %>% 
  filter(!grepl('reverse', description)) %>% 
  arrange(WAIC)

kable(waic.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```

<br><br/>

#### Reversible Jump MCMC:
```{r, echo = F, results='asis'}

# rev.models<-model.results[grepl('fm9', names(model.results)) | grepl('fm10', names(model.results))]
rev.models<-model.results[grepl('reverse', descriptions) ]
rev.names<-names(rev.models)

rev.ind.list<-lapply(rev.models, function(x) x$samples[,grepl('ind', colnames(x$samples))])
rev.ind.means<-lapply(rev.ind.list, function(x) apply(x,2,mean))

tables<-as.list(rep(NA,3))
for(i in 1: length(rev.ind.means)){
  label<-names(rev.ind.means[i])
  model<-descriptions[[label]]
  sum.temp<-tibble(cov = names(rev.ind.means[[i]]), indicator_mean = round(rev.ind.means[[i]],5)) %>% 
    arrange(-indicator_mean)
  cat(label,'    model:',model,'\n')
  temp.tab<-kable(sum.temp) %>%
    kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
  print(temp.tab)
}

```

<br><br/>
<br><br/>
<div>

### Model summaries:

```{r, include = F}
#############################################################################################################################
## model sc.fm1
plot.model<-models[[1]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'lam0') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)




 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )

kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```






### `r in.param<-model.names[[1]]; in.param`



```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`



```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`



```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}


</div>
<br><br><br><br><br>
<div>

```{r, include = F}
#############################################################################################################################
## model sc.fm2
plot.model<-models[[2]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'beta0.lam0', 'beta.lam0[1]') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)


 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )
kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```




### `r in.param<-model.names[[1]]; in.param`

```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`

```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`

```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`

```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[5]]; in.param`

```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}


</div>
<br><br><br><br><br>
<div>

```{r, include = F}
#############################################################################################################################
## model sc.fm2.1
plot.model<-models[[3]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'beta0.lam0', 'beta.lam0[1]') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)


 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )
kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```


### `r in.param<-model.names[[1]]; in.param`



```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`



```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`



```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[5]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}


</div>
<br><br><br><br><br>
<div>

```{r, include = F}
#############################################################################################################################
## model sc.fm2.2
plot.model<-models[[4]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'beta0.lam0', 'beta.lam0[1]') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)


 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )

kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```




### `r in.param<-model.names[[1]]; in.param`



```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`



```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`



```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[5]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}




</div>
<br><br><br><br><br>
<div>

```{r, include = F}
#############################################################################################################################
## model sc.fm3
plot.model<-models[[5]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'beta0.lam0', 'beta.lam0[1]',  'beta.lam0[2]') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)


 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )

kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```



### `r in.param<-model.names[[1]]; in.param`



```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`



```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`



```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[5]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[6]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}


</div>
<br><br><br><br><br>
<div>

```{r, include = F}
#############################################################################################################################
## model sc.fm4
plot.model<-models[[6]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'beta0.lam0', 'beta.lam0[1]',  'beta.lam0[2]',  'beta.lam0[3]') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)


 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )

kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```



### `r in.param<-model.names[[1]]; in.param`



```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`



```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`



```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[5]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[6]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[7]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}

</div>
<br><br><br><br><br>
<div>

```{r, include = F}
#############################################################################################################################
## model sc.fm5
plot.model<-models[[7]]
plot.dat<-model.results[[plot.model]]$samples[,c('N', 'D', 'sigma', 'beta0.lam0', 'beta.lam0[1]',  'beta.lam0[2]','beta.lam0[3]', 'beta.lam0[4]') ]
plot.mcmc<-as.mcmc(plot.dat)
plot.gg<-ggs(plot.mcmc)

```



### `r plot.model` &nbsp;&nbsp; summary:
`r descriptions[plot.model]`

##  {.tabset}

### summary table
```{r, echo = F}
## summary table
model.names<-colnames(plot.dat)
model.modes<-apply(plot.dat, 2, catch.map_estimate)
model.mean<-round(apply(plot.dat,2,mean), 3)
n.eff<-round(effectiveSize(plot.mcmc), 0)
hdi<-apply(plot.dat,2,FUN = ci,method = "HDI")

lower<-round(c(unlist(lapply(hdi,function(x) x$CI_low))), 2)
upper<-round(c(unlist(lapply(hdi,function(x) x$CI_high))),2)

bayes.p<-apply(plot.mcmc,2,catch.p_map)


 
summary.table<-tibble(param = model.names, 
                      n_effective = n.eff, 
                      mean = model.mean, 
                      mode = model.modes, 
                      hdi_89pct_lower = lower, 
                      hdi_89pct_upper = upper, 
                      bayes_P = bayes.p
                      )

kable(summary.table) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")
```



### `r in.param<-model.names[[1]]; in.param`



```{r, echo=F}
#in.param<-model.names[[1]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[2]]; in.param`



```{r, echo=F}
#in.param<-model.names[[2]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```


### `r in.param<-model.names[[3]]; in.param`



```{r, echo=F}
#in.param<-model.names[[3]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[4]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[5]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[6]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[7]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

### `r in.param<-model.names[[8]]; in.param`



```{r, echo=F}
#in.param<-model.names[[4]]
gg.temp<-plot.gg %>% 
  filter(Parameter == in.param)
#ggs_traceplot(gg.temp)
p1<-ggs_traceplot(gg.temp)
p2<-ggs_density(gg.temp)
p3<-ggs_autocorrelation(gg.temp)
grid.arrange(p1, p2, p3,layout_matrix = rbind(c(1, 1),
                        c(3,4)))
```

# {-}


</div>
